---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    fig_caption: yes
    keep_md: yes
    number_sections: yes
---

#Introduction
## File Structure of Commit
* activity.zip - Zipped dataset.
* Assignment1.md - Produced markdown file.
* Assignment1.Rmd - This R markdown file.
* Assignment1_files - Directory were all figures that are produced are stored.
* README.md - Included readme file for assignment.
* src - Directory containing all the code used for the analysis.

## Loading and preprocessing the data
The code for unzipping, loading and preprocessing is found in src/IO.R.

Code in src/IO.R:
```{r echo=FALSE}
src <- file('src/IO.R', 'rt')
print(readLines(src, warn=FALSE))
close(src)
```

Loading data:
```{r}
source('src/IO.R')
```

#Analysis Results
## What is mean total number of steps taken per day?
The code for this section is found in 
src/daily_stats.R and src/hist_daily.R.

Code in src/daily_stats.R:
```{r echo=FALSE}
src <- file('src/daily_stats.R', 'rt')
print(readLines(src, warn=FALSE))
close(src)
```

Code in src/hist_daily.R:
```{r echo=FALSE}
src <- file('src/hist_daily.R', 'rt')
print(readLines(src, warn=FALSE))
close(src)
```

Creating histogram and outputs mean/median for # of steps/day:
```{r}
source('src/hist_daily.R')
```

## What is the average daily activity pattern?
The code for this section is found in 
src/daily_stats.R and src/daily_pattern.R.

Code in src/daily_stats.R:
```{r echo=FALSE}
src <- file('src/daily_stats.R', 'rt')
print(readLines(src, warn=FALSE))
close(src)
```

Code in src/daily_pattern.R:
```{r echo=FALSE}
src <- file('src/daily_pattern.R', 'rt')
print(readLines(src, warn=FALSE))
close(src)
```

Creating plot of the daily interval pattern and output the interval with maximum activity.:
```{r}
source('src/daily_pattern.R')
```

## Imputing missing values
I chose to impute data as a function of interval. For any interval with an NA, I replaced the NA with the average number of steps from the previous plot. Because of this I reuse one function from src/daily_stats.R.

Code for imputing data:
```{r echo=FALSE}
src <- file('src/imputing_data.R', 'rt')
print(readLines(src, warn=FALSE))
close(src)
```

Imputing data:
```{r}
source('src/imputing_data.R')
```

Again I have reused the sum function from the first histogram above. The function can be found in src/daily_stats.R

Creating histogram and outputs mean/median for # of steps/day:
```{r}
source('src/hist_daily_impute.R')
```

The mean and median for the number of steps taken each day has increased after imputing values. The mean increased significantly while the median increased by only a small amount. This makes sense since the NAs were producing more days with less activity than would have been normally measured.

## Are there differences in activity patterns between weekdays and weekends?
This code reused the interval averaging function from src/daily_stats.R to find the average activity throughout the day as a function of weekend and weekday. 

Code for assigning weekdays:
```{r echo=FALSE}
src <- file('src/weekday_analysis.R', 'rt')
print(readLines(src, warn=FALSE))
close(src)
```

Assigning weekdays to imputed dataframe and plotting average activity profile for weekdays and weekends:
```{r}
source('src/weekday_analysis.R')
```

